Gas Dynamics of the Einstein ring RXSJ1131-1123 at $z$=0.654

### 2016-03-29 WRITEUP/Intro.tex
before linewrap

\citestyle{aa}
\shorttitle{TBD}
\shortauthors{Leung}

@@

\title{}
\author{Draft}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

@@

\section{Introduction} 
The gravitational lens RXJ 1131-1231 was discovered with spectroscopic
redshifts of the lens and the QSO are $z_{\rm L}$ = 0.295 and
$z_\textrm{AGN,HST}$ = 
0.658, respectively \citep{

@@

\section{Observations}
\subsection{PdBI} \label{sec:PdBIdata}
Observations of the CO($J$ = 2 $\rightarrow$ 1) rotational line ($\nu_{\rm
rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 0.654
 were carried out using IRAM Plateau de Bure Interferometer (PdBI) at the
(Program ID: S14BX001; PI: D. Riechers). 
 Two observing runs were carried out on 2014 Dec 06 and 2015 Feb 05 under good
weather conditions in the C and D array configurations, respectively. The 2 mm
receivers were used to cover the redshifted CO($J$ = 2 $\rightarrow$ 1) line
and the 
underlying continuum emission (rest-frame 3.6 mm), employing
a correlator setup providing an effective bandwidth of 3.6 GHz and spectral 
resolution of 10.0 MHz ($\sim$21.5281 km s$^{-1}$).
This resulted in 3.74 hours of cumulative six antenna-equivalent on-source time
after discarding unusable visibility data.
% D: 1.5 hours; 1055+018 (BP) , 3C279 (RF, fixed flux), 1127-145 (phase/amp),
% 1124-186(ditto)
% C: 2.2 hours; MWC349 (fixed flux), 1055+018 (RF = bandpass), 1124-186
% (phase/amp), 1127-145 (ditto)
% total: 3.75 hours
%For both tracks, 
The nearby quasars 1127$-$145 and 1124$-$186 were observed every BLAH minutes
for
pointing, secondary amplitude, and phase calibration and 1055$+$018 was observed as bandpass calibrators 
for both tracks.
MWC349 and 3C279 were observed
as the primary
absolute flux calibrator for C and D array observations, respectively, yielding $\lesssim
$15\% calibration accuracy.

>>>>

\citestyle{aa}
\shorttitle{TBD}
\shortauthors{Leung \& Riechers}

@@

\title{Gas Dynamics of the Einstein ring RXSJ1131-1123 at $z$=0.654}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; \myemail}

@@

\section{Introduction} 
The gravitational lens RXJ 1131-1231 was discovered with spectroscopic
redshifts of the lens and the QSO are $z_{\rm L}$ = 0.295 and
$z_\textrm{AGN,HST}$ = 
0.658, respectively \citep{}

@@

\section{Observations}
\subsection{PdBI} \label{sec:PdBIdata}
Observations of the CO($J$ = 2 $\rightarrow$ 1) rotational line ($\nu_{\rm
rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 0.654
 were carried out using IRAM Plateau de Bure Interferometer (PdBI) at the
(Program ID: S14BX001; PI: D. Riechers). 
 Two observing runs were carried out on 2014 Dec 06 and 2015 Feb 05 under good
weather conditions in the C and D array configurations, respectively. The 2 mm
receivers were used to cover the redshifted CO($J$ = 2 $\rightarrow$ 1) line
and the 
underlying continuum emission (rest-frame 3.6 mm), employing
a correlator setup providing an effective bandwidth of 3.6 GHz and spectral 
resolution of 10.0 MHz ($\sim$21.5281 km s$^{-1}$).
This resulted in 3.74 hours of cumulative six antenna-equivalent on-source time
after discarding unusable visibility data.
% D: 1.5 hours; 1055+018 (BP) , 3C279 (RF, fixed flux), 1127-145 (phase/amp),
% 1124-186(ditto)
% C: 2.2 hours; MWC349 (fixed flux), 1055+018 (RF = bandpass), 1124-186
% (phase/amp), 1127-145 (ditto)
% total: 3.75 hours
%For both tracks, 
The nearby quasars 1127$-$145 and 1124$-$186 were observed every 22 minutes
for
pointing, secondary amplitude, and phase calibration and 1055$+$018 was observed as bandpass calibrators 
for both tracks.
MWC349 and 3C279 were observed
as the primary
absolute flux calibrator for C and D array observations, respectively, yielding $\lesssim
$15\% calibration accuracy.
